Report on Lab 1 \& Lab 2 in EDA282, Parallel Computer Organization and Design

### 2014-10-12 lab/report/include/lab2.tex
Appendices added, or something.

\centerline{
\begin{minipage}{1.0\textwidth}
\lstinputlisting[caption={\textit{Parallel version of original} \texttt{void Solve(double **A).}}, label={lst:solve}]{include/solve.c}
\end{minipage}
}
\subsection{Task 3}
\todo[inline]{
Evaluate MSI, MESI, and MESI+migratory in the context of this benchmark. Perform a detailed characterization of the benchmark using different protocols. Discuss how the behavior changes when the working set size is modified. Show how execution time relates to the cache access statistics.}

Samma mönster som i Lab 1, MSI får mer writemiss osv än MESI vilket gör MESI lite bättre.
\begin{figure}[t]
	\center
	\includegraphics[width=0.8\textwidth]{lab2bars}
	\caption{Results from simulation of the parallelized benchmark for all cache coherence protocols combined with different working sets.}
	\label{fig:resultslab1}
\end{figure}

>>>>

\subsection{Task 3}
\todo[inline]{
Evaluate MSI, MESI, and MESI+migratory in the context of this benchmark. Perform a detailed characterization of the benchmark using different protocols. Discuss how the behavior changes when the working set size is modified. Show how execution time relates to the cache access statistics.}

In \reffig{fig:lab2} the results from running the parallelized version of the program in the simulator with the different CCP:s and three different matrix dimensions.

DRAFTY:
MESI gains on MSI with big working sets as the working set does not fit in the cache and in MSI every readMiss will fetch the line into Shared state and then move to modified causing a invalidate to be sent. In MESI this is skipped as the readMiss will fetch the line into Exclusive state and then Modified not causing any invalidates to be sent.

\begin{figure}[t]
	\center
	\includegraphics[width=0.8\textwidth]{lab2bars}
	\caption{Results from simulation of the parallelized benchmark for all cache coherence protocols combined with different working sets.}
	\label{fig:lab2}
\end{figure}
